---
title: "Data Importing"
author: "Junyan Zhu"
data: "2022-09-20"
output: 
  github_document: default
---

```{r}
```{r}
library(tidyverse)
library(readxl)
library(haven)
```


## Data Import: CSVs

Let's import data using the `readr` package

```{r}
library(tidyverse)
library(read_excel)
litters_df = read.csv("./data_import_examples/FAS_litters.csv")
litters_df = janitor::clean_names(litters_df)
```

look at data
```{r}
litters_df
```


```{r}
skimr::skim(litters_df)
```

`read_csv` options

```{r}
read_csv("./data_import_examples/FAS_litters.csv")
```


##other file formats

we need to read in an excel spreadsheet

```{r}
library(tidyverse)
library(readxl)
mlb_df = read_excel("./data_import_examples/mlb11.xlsx",
                    range = "B3:D6")

mlb_df
```

```{r}
view(mlb_df)
```


```{r}
lotr_words_df = 
  read_excel(
    "./data_import_examples/LotR_Words.xlsx"
  )

lotr_words_df
```

##Still more formats...

Read in a SAS dataset

```{r}
library(tidyverse)
library(readxl)
library(haven)
pulse_df = read_sas("./data_import_examples/public_pulse_data.sas7bdat")
```

